$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-08 paper/paper.tex
Move the equivalent congruence relation to the body

We define the base cases of a structural congruence relation \textsc{StructCong} $\eqeq$ in \autoref{fig:struct-cong-base}.
Its congruent equivalence closure \textsc{Equals} $\eq{}$ is defined in \autoref{app:struct}.

@@

>>>>

We define the base cases of a structural congruence relation \textsc{StructCong} $\eqeq$ in \autoref{fig:struct-cong-base}.

@@

We lift the relation \textsc{StrucCong} $\eqeq{}$ and close it under equivalence and congruence in \textsc{Equals} $\eq{}$ as shown in \autoref{fig:struct-cong1}.
The $\func{cong-}$* rules define structural congruence under a context $\mathcal{C}[\cdot]$ \cite{Sangio01}, respectively restriction, composition, input and output.
The remaining three rules close structural congruence under reflexivity, symmetry and transitivity. 
The transitivity rule makes it tricky to prove predicates by induction on \textsc{Equals}: Agda cannot immediately see that such doubly recursive calls terminate.
In order to remedy this, we model the inductive structure syntactically and index \textsc{Equals} by a type \textsc{Rec}.

\begin{figure}[h]
  \begin{mathpar}
    \datatype
    { }
    {\Rec : \Set}
    \; \textsc{Rec}

    \inferrule
    { }
    {\constr{zero} : \Rec}

    \inferrule
    {r : \Rec}
    {\constr{one} \; r : \Rec}

    \inferrule
    {r \; s : \Rec}
    {\constr{two} \; r \; s : \Rec}

    \datatype
    {P \, Q : \Process_n \\ r : \Rec}
    {P \eq{r} Q : \Set}
    \; \textsc{Equals}

    \inferrule
    {eq : P \eqeq Q}
    {\constr{struct} \; eq : P \eq{\constr{zero}} Q}

    \inferrule
    {eq : P \eq{r} P'}
    {\constr{cong-scope} \; eq : \new P \eq{\constr{one} \; r} \new P'}

    \inferrule
    {eq : P \eq{r} P'}
    {\constr{cong-comp} \; eq : \comp{P}{Q} \eq{\constr{one} \; r} \comp{P'}{Q}}

    \inferrule
    {eq : P \eq{r} P'}
    {\constr{cong-recv} \; eq : \recv{x}P \eq{\constr{one} \; r} \recv{x}P'}

    \inferrule
    {eq : P \eq{r} P'}
    {\constr{cong-send} \; eq : \send{x}{y}P \eq{\constr{one} \; r} \send{x}{y}P'}

    \inferrule
    { }
    {\constr{refl} : P \eq{\constr{zero}} P}

    \inferrule
    {eq : P \eq{r} Q}
    {\constr{sym} \; eq : Q \eq{\constr{one} \; r} P}

    \inferrule
    {eq_1 : P \eq{r} Q \\ \; eq_2 : Q \eq{s} R}
    {\constr{trans} \; eq_1 \; eq_2 : P \eq{\constr{two} \; r \; s} R}
\end{mathpar}
\caption{Structural rewriting rules lifted to a congruent equivalence relation indexed by a recursion tree.}
\label{fig:struct-cong1}
\end{figure}
